%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Experimental Setup and Simulation Methods}
\label{ch:expsetup}

In this chapter, I will discuss the instrument and optical setup used, along with details on sample and tip preparation. I will also discuss the \ac{DFT} details, including the software package, potential approximation method, and basis set used. The results of the \ac{DFT} calculation are qualitatively compared with the experimental results.

%\section{Low vibration facility}

\section{The microscope}

All experimental measurements were made on an Omicron \ac{UHV} low temperature \ac{SPM}. Experimental data was obtained at liquid helium temperatures ($\sim \SI{4.5}{K}$) and at pressures below $1 \times 10^{-11}$ mbar. 

The entire microscope is inside of an ultra-low vibration facility (dubbed ``the pod"), where it sits on a $\sim \SI{36}{tonne}$ inertial concrete block that is resting on six pneumatic isolators. To further decouple vibrations from the main building from the microscope, the pod is surrounded by a double-walled concrete enclosure containing acoustically isolating material, and rests on a foundation separate from the main building. Small feed-through openings allow wires to be passed from the microscope to a control unit outside the pod. The microscope can then be remotely operated using a computer in a separate control room.

The microscope is composed of two main chambers, each of which will be discussed below.


\subsection{Preparation chamber}

The preparation chamber is

ith pressures maintained at around $1 \times 10^{-9}$ mbar. The presence of cryogens in the measurement 

\subsubsection{Substrates}

\subsubsection{Molecules}



\subsection{Low-temperature chamber}



\subsection{Tip preparation}
In order to prepare 



\section{Optical setup}






\section{Density functional theory methods}

Molecular orbital and energy level of free molecules are calculated using \ac{DFT} package \emph{Gaussian 16} \citep{frisch2016gaussian}. Before the single-point


%%%%%
